\documentclass[12pt,a4paper,oneside]{report}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[a4paper,left=3.5cm,right=2.5cm,top=3cm,bottom=3cm]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{tabularx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{setspace}
\usepackage{enumitem}

% Update these fields before formal submission.
\newcommand{\thesistype}{Bachelor Thesis}
\newcommand{\thesistitle}{Design and Implementation of Anhoc}
\newcommand{\thesissubtitle}{A Web-Based Mathematics Learning Platform for Structured Learning, Adaptive Practice, and Progress Tracking}
\newcommand{\thesisstudent}{Your Name}
\newcommand{\thesisstudentid}{Your Student ID}
\newcommand{\thesisspecialty}{Information and Communication Technology}
\newcommand{\thesissupervisor}{Your Supervisor}
\newcommand{\thesislocation}{Ho Chi Minh City}
\newcommand{\thesismonthyear}{June 2026}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  pdftitle={Design and Implementation of Anhoc},
  pdfauthor={Your Name}
}

\graphicspath{{docs/thesis/chapters/}{docs/thesis/}{docs/images/}{docs/}}
\setstretch{1.2}
\setlength{\parindent}{1.5em}
\setlength{\parskip}{0.35em}
\setlist[itemize]{topsep=0.35em,itemsep=0.15em}
\setlist[enumerate]{topsep=0.35em,itemsep=0.15em}

\newcommand{\code}[1]{\nolinkurl{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

\lstdefinestyle{thesiscode}{
  basicstyle=\ttfamily\small,
  breaklines=true,
  columns=fullflexible,
  keepspaces=true,
  frame=single,
  rulecolor=\color{black!20}
}

\begin{document}

\hypersetup{pageanchor=false}
\begin{titlepage}
\thispagestyle{empty}
\begin{center}
{\Large UNIVERSITY OF SCIENCE AND TECHNOLOGY OF HANOI\par}
\vspace{0.35cm}
{\large BACHELOR'S DEGREE\par}

\vspace{2.1cm}
{\LARGE \textbf{\thesistype}\par}

\vspace{1.25cm}
{\large by\par}
\vspace{0.4cm}
{\Large \textbf{\thesisstudent}\par}
{\large \thesisstudentid\par}
\vspace{0.3cm}
{\large \thesisspecialty\par}

\vspace{1.6cm}
{\large Title:\par}
\vspace{0.35cm}
{\Large \textbf{\thesistitle}\par}
\vspace{0.5cm}
{\large \thesissubtitle\par}

\vspace{1.8cm}
\begin{tabular}{rl}
Supervisor: & \thesissupervisor \\
Project basis: & Anhoc web application repository \\
Implementation scope: & \code{frontend/}, \code{backend/}, and \code{chatbot/}
\end{tabular}

\vfill
{\thesislocation. \thesismonthyear\par}
\end{center}
\end{titlepage}

\chapter*{Declaration}
\thispagestyle{empty}
I hereby declare that this thesis titled \textit{\thesistitle} is prepared from the implemented
Anhoc repository and the accompanying project documentation. All architectural descriptions,
feature summaries, and implementation details presented in this report are derived from the
inspected codebase, and external concepts or technologies are cited where appropriate.

To the best of my knowledge, this report does not intentionally reproduce uncited work as an
original contribution. Any frameworks, libraries, documents, or external references used in the
preparation of this thesis are acknowledged in the bibliography.

\vfill
\begin{flushright}
\thesislocation, \thesismonthyear\\[2cm]
\textbf{\thesisstudent}
\end{flushright}

\chapter*{Acknowledgements}
\thispagestyle{empty}
This thesis was prepared from the current Anhoc web application repository. The document reflects
the work embodied in the frontend, backend, database, and chatbot modules, as well as the
supporting technical design notes maintained with the project.

I would like to acknowledge the contributors who shaped the platform's architecture, educational
workflows, and deployment configuration, together with the maintainers of the open-source tools
that made the system possible, including Next.js, React, Express, Prisma, PostgreSQL, and the
supporting Python ecosystem used by the tutoring service.

\vfill
\begin{flushright}
(\thesisstudent)\\
\thesislocation, \thesismonthyear
\end{flushright}
\clearpage
\tableofcontents
\thispagestyle{empty}

\clearpage
\pagenumbering{roman}
\setcounter{page}{1}

\chapter*{List of Acronyms}
\addcontentsline{toc}{chapter}{List of Acronyms}
\begin{longtable}{L{0.22\textwidth}L{0.68\textwidth}}
\textbf{API} & Application Programming Interface \\
\textbf{BYOK} & Bring Your Own Key \\
\textbf{CORS} & Cross-Origin Resource Sharing \\
\textbf{JWT} & JSON Web Token \\
\textbf{LLM} & Large Language Model \\
\textbf{ORM} & Object-Relational Mapping \\
\textbf{RBAC} & Role-Based Access Control \\
\textbf{REST} & Representational State Transfer \\
\textbf{UI} & User Interface \\
\textbf{XP} & Experience Points \\
\end{longtable}

\clearpage
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures

\clearpage
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables

\clearpage
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
Anhoc is a web-based mathematics learning platform designed for structured school-level study. The
implemented system combines bilingual lesson content, dynamically generated practice exercises,
grade-level tests, progression tracking, administrative management, notifications, multiplayer and
single-player math games, and an integrated tutoring chatbot. This thesis documents the design
and implementation of Anhoc based on the current repository contents.

The software follows a service-oriented web architecture. A Next.js frontend provides the student
and administrative interfaces. An Express backend exposes REST endpoints for authentication,
lessons, tests, achievements, notifications, games, supervisor workflows, and subscription
management. Prisma is used as the persistence layer, PostgreSQL stores the core application
state, and a companion Python chatbot service extends the platform with conversational tutoring
capabilities.

A notable implementation decision is the use of persisted question snapshots. Reusable templates
define how questions are generated, while snapshots preserve the exact generated variables,
accepted answers, and scoring outcomes for each attempt. This design supports reproducible
grading, debugging, review, and reporting. The project also adopts dynamic role-based access
control with subject-level restrictions, progression services for mastery and XP, and operational
support for learn units and subscription-oriented platform management.

This thesis presents the problem context, requirements, system architecture, data model,
implementation details, and an evaluation of the current solution. It also discusses limitations
and practical improvements required to mature the platform further as an educational software
system.

\textbf{Keywords:} mathematics learning platform, question generation, role-based access control,
progress tracking, tutoring chatbot, web application architecture

\clearpage
\hypersetup{pageanchor=true}
\pagenumbering{arabic}

\input{chapters/introduction}
\input{chapters/requirements}
\input{chapters/design}
\input{chapters/implementation}
\input{chapters/evaluation}
\input{chapters/conclusion}
\input{chapters/appendix}

\begin{thebibliography}{99}
\bibitem{anhoc-readme}
Anhoc project repository overview, \code{README.md}.

\bibitem{frontend-package}
Anhoc frontend package manifest and framework dependencies, \code{frontend/package.json}.

\bibitem{backend-package}
Anhoc backend package manifest and runtime dependencies, \code{backend/package.json}.

\bibitem{nextjs-docs}
Vercel. \textit{Next.js Documentation: App Router}. Available at:
\url{https://nextjs.org/docs/app}. Accessed June 15, 2026.

\bibitem{react-docs}
Meta Platforms, Inc. and contributors. \textit{React Documentation}. Available at:
\url{https://react.dev/learn}. Accessed June 15, 2026.

\bibitem{express-docs}
OpenJS Foundation and Express contributors. \textit{Express.js 5.x API Reference}. Available at:
\url{https://expressjs.com/en/api/}. Accessed June 15, 2026.

\bibitem{prisma-docs}
Prisma. \textit{Prisma ORM Documentation}. Available at:
\url{https://www.prisma.io/docs/orm}. Accessed June 15, 2026.

\bibitem{postgresql-docs}
PostgreSQL Global Development Group. \textit{PostgreSQL 18 Documentation}. Available at:
\url{https://www.postgresql.org/docs/current/index.html}. Accessed June 15, 2026.

\bibitem{jwt-rfc}
M. Jones, J. Bradley, and N. Sakimura. \textit{RFC 7519: JSON Web Token (JWT)}.
RFC Editor, May 2015. Available at: \url{https://www.rfc-editor.org/info/rfc7519/}.

\bibitem{jwt-bcp}
N. Sheffer, D. Hardt, and M. Jones. \textit{RFC 8725: JSON Web Token Best Current Practices}.
RFC Editor, February 2020. Available at: \url{https://www.rfc-editor.org/info/rfc8725/}.

\bibitem{mathjs-docs}
\textit{mathjs Documentation}. Available at: \url{https://mathjs.org/docs/}. Accessed June 15, 2026.

\bibitem{nextintl-docs}
Jan Amann and contributors. \textit{next-intl Documentation: Getting Started}. Available at:
\url{https://next-intl.dev/docs/getting-started}. Accessed June 15, 2026.

\bibitem{backend-server}
Anhoc backend bootstrap implementation, \code{backend/server.ts}.

\bibitem{backend-schema}
Anhoc database schema and Prisma models, \code{backend/prisma/schema.prisma}.

\bibitem{backend-auth}
Anhoc authentication and authorization middleware, \code{backend/middleware/auth.ts}.

\bibitem{backend-math}
Anhoc math generation and answer evaluation service, \code{backend/services/mathService.ts}.

\bibitem{chatbot-spec}
Anhoc tutoring chatbot specification and implementation, \code{chatbot/SPEC.md},
\code{chatbot/README.md}, and \code{chatbot/main.py}.

\bibitem{chatbot-widget}
Anhoc tutoring widget integration in the frontend, \code{frontend/src/components/feature/ChatbotWidget.tsx}.

\bibitem{technical-design}
Anhoc technical design document, \code{docs/TDD/technical-design.md}.
\end{thebibliography}

\end{document}
