\chapter{Conclusion \& Perspective}

This thesis documented the design and implementation of Anhoc, a web-based mathematics learning platform that combines bilingual lesson content, generated practice exercises, grade-level assessments, progression tracking, and administrative control. The implemented system uses a modern web stack with a Next.js frontend, an Express backend, Prisma as the persistence layer, and PostgreSQL as the database.

The project demonstrates several sound software engineering decisions. Most importantly, it separates reusable question templates from persisted question snapshots, enabling reproducible grading and better issue reporting. It also uses a dynamic access-control model and a modular progression pipeline for mastery, XP, and achievements. These choices make the system more extensible than a minimal educational CRUD application.

At the same time, the current implementation remains an evolving platform rather than a finished production learning system. It still needs broader automated testing, stronger validation of author-authored template logic, clearer schema ownership, and empirical studies of educational effectiveness.

Several directions for further development are especially important. First, the platform should enrich its learning-data pool by expanding the number of lessons, question templates, difficulty bands, and learner-interaction records available for analysis. A larger and more diverse dataset would improve content coverage, make recommendation or adaptive features more reliable, and support more meaningful educational evaluation. Second, the user experience can be refined through more intentional animation and motion design. Rather than using animation only for visual appeal, future iterations should employ it carefully to guide attention, clarify transitions, and make the platform feel welcoming without creating distraction or reward dependency.

Third, deployment should move through a staged product-release process rather than jumping directly into unrestricted public use. An internal alpha phase can validate technical stability and content correctness, a closed beta phase can collect structured feedback from a limited group of students or teachers, and an open beta phase can then test broader usability, engagement, and infrastructure readiness under more realistic traffic. Fourth, the project should create formal evaluation survey forms and feedback instruments so that learners, teachers, and supervisors can provide collective opinions about usability, enjoyment, clarity, pacing, and perceived learning value. Such feedback would complement technical testing with human-centered evidence.

Finally, future work should address operational sustainability. This includes pricing-model design, infrastructure cost estimation, maintenance planning, content revision workflows, and support procedures for running the platform over time. These concerns are essential if Anhoc is to evolve from a technically promising prototype into a maintainable educational product. Even with its current limitations, the project is a strong foundation for future academic work and practical product development in mathematics learning software.
