\section{System Implementation}

\subsection{Frontend Implementation}

The frontend is implemented with Next.js and TypeScript. The app-router structure separates student and administrative workflows into route segments, while service modules in \code{frontend/src/services} centralize communication with the backend.

Important frontend concerns include:
\begin{itemize}
  \item authentication bootstrap and persistence;
  \item protected routes and permission checks;
  \item lesson and practice page composition;
  \item test flows with answer submission and result presentation;
  \item admin screens for users, roles, reports, and dashboards.
\end{itemize}

The component structure indicates a feature-oriented approach rather than a single monolithic page design. Examples include \code{QuestionPlayer.tsx}, \code{PracticeResultModal.tsx}, \code{AchievementGallery.tsx}, and \code{CreateTemplateModal.tsx}.

\subsection{Backend API Implementation}

The backend exposes versioned REST endpoints. Table \ref{tab:api-areas} groups the major API areas.

\begin{table}[H]
\centering
\caption{Main API groups}
\label{tab:api-areas}
\begin{tabularx}{\textwidth}{L{0.22\textwidth}Y}
\toprule
\textbf{API Group} & \textbf{Purpose} \\
\midrule
\code{/api/v1/auth} & Registration, login, profile retrieval, password change, and activity endpoints. \\
\code{/api/v1/lessons} & Lesson, grade, subject, mastery, practice initiation, and study-time endpoints. \\
\code{/api/v1/tests} & Grade tests, attempt detail, answer submission, finish flow, template management, and report workflow. \\
\code{/api/v1/admin} & Users, roles, access control, insights, and dashboard statistics. \\
\code{/api/v1/achievements} & Achievement seeding, listing, earned-state retrieval, and re-checking. \\
\bottomrule
\end{tabularx}
\end{table}

The API design is pragmatic. It is expressive enough for the frontend and explicit enough for debugging, while remaining simple to secure and deploy.

\subsection{Question Generation and Grading}

The file \code{backend/services/mathService.ts} contains a central part of the project: logic-driven variable generation and answer evaluation. The implementation uses the \code{mathjs} expression engine for parsing and evaluating formulas, derived expressions, and constraints \cite{mathjs-docs}. The service supports several rule types:
\begin{itemize}
  \item fixed numeric values;
  \item arrays of possible values;
  \item numeric ranges with optional step and precision;
  \item random choices from configured lists;
  \item derived expressions evaluated from previously generated variables;
  \item constraints that must hold before a question is accepted.
\end{itemize}

The generation flow can be summarized as:
\begin{enumerate}
  \item parse the stored \code{logic\_config};
  \item generate variables from configured rules;
  \item apply derived expressions;
  \item verify constraints;
  \item repeat until a valid assignment is found or a maximum number of attempts is reached.
\end{enumerate}

Answer checking supports multiple cases:
\begin{itemize}
  \item numeric answers, compared with a small tolerance;
  \item boolean answers, normalized from common textual forms;
  \item text or structured answers, normalized for comparison;
  \item multiple accepted formulas for the same question.
\end{itemize}

This is a stronger implementation than a naive string-equality checker because it tolerates common input variance while still grounding correctness in mathematically evaluated formulas.

\subsection{Attempt Lifecycle}

The implemented attempt lifecycle is one of the most important interactions in the system.

\subsubsection*{Practice Start}

When a student starts practice for a lesson:
\begin{enumerate}
  \item the backend validates lesson existence and subject access;
  \item it loads lesson templates;
  \item it generates variables and right answers for selected templates;
  \item it creates a \code{test\_attempt} record;
  \item it bulk-inserts \code{question\_snapshots};
  \item it returns a stable attempt payload to the frontend.
\end{enumerate}

\subsubsection*{Answer Submission}

When a student submits an answer:
\begin{enumerate}
  \item the backend loads the snapshot and template;
  \item it evaluates the answer using either text comparison or formula-based checking;
  \item it updates the stored snapshot with answer and correctness state;
  \item it returns correctness information and explanation content.
\end{enumerate}

\subsubsection*{Attempt Completion}

When an attempt is finished:
\begin{enumerate}
  \item unanswered snapshots are marked incorrect;
  \item correct answers are counted and the final score is computed;
  \item lesson mastery is updated when the attempt is linked to a lesson;
  \item XP is awarded and logged;
  \item aggregate student statistics are recalculated;
  \item achievements are re-evaluated and may award additional XP.
\end{enumerate}

This completion pipeline shows that the project treats scoring as part of a broader progression workflow rather than as an isolated calculation.

\subsection{Administrative Implementation}

The administrative subsystem includes user and role management, subject permission management, dashboard statistics, and question report review. The route design suggests that administrators can change both coarse and fine-grained access behavior without redeploying the application.

This is reinforced by the underlying data model:
\begin{itemize}
  \item \code{roles} store named roles;
  \item \code{actions} and \code{resources} define the authorization vocabulary;
  \item \code{role\_permissions} map actions to resources per role;
  \item \code{role\_subject\_permissions} restrict which subjects a role can manage.
\end{itemize}

This structure scales better than a hard-coded permission matrix embedded directly in frontend components.

\subsection{Configuration and Deployment}

The repository defines environment variables for both frontend and backend execution. Examples include:
\begin{itemize}
  \item API base URLs and rewrite targets for the frontend;
  \item \code{DATABASE\_URL}, \code{JWT\_SECRET}, and \code{CORS\_ORIGINS} for the backend;
  \item \code{AUTO\_SEED\_ACHIEVEMENTS} to control whether achievement definitions are seeded automatically.
\end{itemize}

The backend startup process explicitly checks the achievement seeding flag before inserting seed data. This is a sound operational choice because it prevents accidental reseeding in every environment.

To support standard containerised hosting on services like Render, the backend includes a custom \texttt{Dockerfile} built on the lightweight \texttt{node:22-alpine} base image. The configuration installs runtime dependencies such as \texttt{openssl} (required for the Prisma Client runtime) and \texttt{curl}. A container health check is declared natively using a Node.js fetch script targeting the backend health endpoint (\code{/api/v1/health}) on the configured port.

A key operational challenge resolved in the deployment configuration involves build-time database constraints. During the Docker compilation phase on Render, the \code{DATABASE\_URL} environment variable is not injected (as it is scoped strictly to the application's runtime phase). The compiler initially failed when executing \code{npx prisma generate} because the local ORM configuration (\code{prisma.config.ts}) tried to resolve this variable dynamically using Prisma's \code{env()} configuration helper, which enforces lookup checks during build time. This constraint was resolved by refactoring the configuration file to reference the standard Node.js \code{process.env.DATABASE\_URL} lookup directly. This adjustment allows the client generation script to execute successfully during image compilation, decoupling the database connectivity verification from the build phase.

\subsection{User Interface Presentation}

The frontend interface features a responsive layout designed for both desktop side navigation and mobile layout constraints. For small screen widths, a floating navigation bar (\code{BottomNav.tsx}) provides touch-friendly route switching between student dashboard, roadmap, practice sessions, chatbot tutor, and settings. To enhance visual separation and ensure the bottom navigation stands out over the dynamic scrolling content, the element implements absolute layout positioning with a top border class (\code{border-t-2}) and dynamic slide-in entry animation.
