\chapter{Introduction}

\section{Background}

Digital learning systems are increasingly expected to do more than present static content. In mathematics education, students need repeated practice, immediate feedback, structured progression, and content that can be adapted to multiple grades and topics. A conventional content website can display lessons, but it does not by itself provide reusable question generation, mastery tracking, or administrative control over subject-specific learning material.

The Anhoc project addresses this gap by combining theory lessons, generated practice, formal test sessions, and gamified progression in a single web application. The project targets school-level mathematics learning and is organized around subjects, grades, and lessons. The implemented system allows a student to read theory content, start practice from lesson templates, submit answers, complete tests, and monitor progress through XP, levels, and achievements. At the same time, an administrator can manage lessons, question templates, user accounts, roles, and access permissions.

\subsection{Statistical Context of E-Learning in Vietnam}

The Vietnamese context makes digital learning a credible opportunity rather than a speculative one. DataReportal reported 79.8 million internet users in Vietnam in January 2025, equivalent to 78.8\% of the population, together with 127 million cellular mobile connections \cite{datareportal-vietnam-2025}. EdTech Hub's 2024 rapid scan, drawing on national statistics, further notes that 96\% of households had a mobile phone, 79\% of households had internet access in 2023, and mobile devices are substantially more common than computers in the home \cite{edtechhub-vietnam-scan}. For a school-age platform, these figures support a mobile-first design assumption: many learners can get online, and many will do so through phones rather than desktop computers.

Children's everyday digital use reinforces that opportunity. UNICEF's Disrupting Harm survey in Vietnam found that 89\% of children aged 12--17 had used the internet in the previous three months, and 87\% of internet-using children used it every day \cite{unicef-disrupting-harm-vietnam-2022}. This does not automatically imply that online learning is effective, but it does mean that digital habits are already deeply embedded in the age group most relevant to school-level learning platforms.

Taken together, these indicators show that Vietnam is participating in the wider global adaptation to digital technology in everyday life, communication, and education. As internet access, mobile-device use, and online habits continue to expand, the need for learning platforms is not decreasing but becoming more immediate. In this environment, educational platforms are increasingly required not only as optional supplements, but as practical tools for delivering accessible, structured, and engaging learning experiences.

\section{Problem Statement}

The educational opportunity in Vietnam is therefore real, but so are the design constraints. Learners are online, many households have mobile phones, and the national education context is already shaped by structured assessment and digital transition. However, the existence of connectivity does not by itself produce a child-friendly, high-quality learning experience.

EdTech Hub's rapid scan shows that Vietnam already has a crowded educational technology landscape that includes online learning platforms, learning apps, websites, open resources, and YouTube channels \cite{edtechhub-vietnam-scan}. In other words, the core problem is not simply the absence of digital content. It is the absence of an integrated platform that is suitable for school-age learners, easy to navigate on mobile devices, and capable of balancing engagement with real learning depth.

This problem has several dimensions. First, fragmented choice can make it difficult for students and families to identify which tools are trustworthy, age-appropriate, and educationally coherent. Second, high-stakes assessment culture can narrow learning into score chasing. A 2025 study in the \textit{Vietnam Journal of Education} found that the proposed 2025 national high school graduation examination could create adverse washback effects, including narrowing learning content and reducing student engagement, even while it strongly motivates score-oriented preparation \cite{vje-washback-2025}. Third, digital products that rely too heavily on repetition, streak pressure, or rapid-fire quizzes may capture attention without supporting durable understanding.

This concern is consistent with international evidence. UNESCO's 2023 Global Education Monitoring Report concludes that excessive or inappropriate technology use can harm learning, and reports that mere proximity to a mobile device was found to distract students and negatively affect learning in 14 countries \cite{unesco-gem-2023}. OECD analysis of PISA 2022 similarly shows that moderate digital-device use for learning can be associated with better mathematics outcomes, whereas leisure-oriented digital use and classroom distraction are associated with lower mathematics performance \cite{oecd-screen-time-2024}. The implication is important for Anhoc: digital learning for children should not imitate the most attention-maximizing parts of social media or shallow quiz apps.

The main engineering problem solved by Anhoc is therefore the design of a learning platform that satisfies four requirements at the same time:
\begin{itemize}
  \item it must support reusable content across grades and subjects;
  \item it must generate exercises dynamically rather than storing every question instance manually;
  \item it must keep each attempt stable enough to be scored, reviewed, and audited later;
  \item it must provide operational control for administrators without hard-coding every permission into the user interface.
\end{itemize}

Many simple practice applications solve only one part of this problem. Some provide content but not progression. Others provide gamification but mostly reward speed, repetition, or daily return behavior. Large-scale online learning platforms often excel at adult or professional self-study, but that model is not automatically suitable for children who need guided progression, lighter cognitive load, and a more playful interface. Anhoc therefore introduces a more child-oriented structure: a friendly web interface, bilingual lesson flow, logic-based question generation, persisted attempt snapshots, dynamic role-based access control, and a progression system intended to make learning engaging without reducing it to streak maintenance.

\subsection{Advantages and Limitations of E-Learning Applications in Vietnam}

The statistical context above suggests several clear advantages for e-learning applications in Vietnam.
\begin{itemize}
  \item \textbf{Large reachable user base:} high internet penetration and widespread mobile connectivity make app-based learning distribution technically feasible at national scale \cite{datareportal-vietnam-2025}.
  \item \textbf{Institutional readiness:} the fact that most schools are already connected to the internet creates a practical foundation for blended learning, school-supported digital homework, and platform-assisted assessment \cite{unesco-vietnam-technology}.
  \item \textbf{Flexible continuity:} emergency distance-learning evidence shows that digital tools, especially when combined with broadcast channels, can preserve instructional continuity during disruption \cite{worldbank-vietnam-tv-learning}.
  \item \textbf{Expanding ecosystem:} the presence of platforms, apps, websites, and video channels indicates that learners and schools are already familiar with multiple forms of educational technology \cite{edtechhub-vietnam-scan}.
\end{itemize}

At the same time, e-learning applications in Vietnam face structural limitations that directly motivate Anhoc's design.
\begin{itemize}
  \item \textbf{Access inequality:} home internet access and device ownership vary sharply by income and geography, which means an app cannot assume stable, private, always-on access for every learner \cite{unesco-vietnam-technology,worldbank-vietnam-distance-learning}.
  \item \textbf{Fragmentation of tools and content:} World Bank analysis of Vietnamese e-learning practice notes underdeveloped, unstandardized platforms and inconsistent learning materials, making quality assurance difficult \cite{worldbank-vietnam-distance-learning}.
  \item \textbf{Weak progression support in basic tools:} many digital offerings can deliver lessons or quizzes but do not reliably connect content, assessment history, progression, and administration in one coherent system.
  \item \textbf{Equity risk:} if platform design ignores device constraints, bandwidth limits, or administrative coordination, digital learning can widen rather than reduce educational inequality \cite{unesco-vietnam-technology,worldbank-vietnam-distance-learning}.
\end{itemize}

These conditions shape the problem statement for Anhoc. A useful platform in Vietnam must not only digitize lessons; it must also provide structured practice, durable assessment records, scalable administration, and a child-friendly design that can stand out in a crowded and often repetitive learning-app landscape.

\section{Objectives}

This thesis has the following objectives:
\begin{itemize}
  \item document the implemented Anhoc system in a thesis-style format;
  \item explain the architecture and data model used by the project;
  \item describe how the platform generates and evaluates mathematical exercises;
  \item analyze how authentication, authorization, and administration are handled;
  \item evaluate the strengths, limitations, and next steps of the current implementation.
\end{itemize}

\section{Scope}

The scope of this thesis is limited to the code and documentation available in the repository. It focuses on the currently implemented frontend, backend, database schema, and operational flows. The thesis does not claim to measure learning outcomes through classroom experimentation, because no such experimental dataset is included in the repository. Evaluation is therefore based on software capabilities, system structure, and scenario-level validation.

\section{Contributions of the Project}

The implemented project contributes several concrete software ideas:
\begin{itemize}
  \item a bilingual lesson structure for educational content in English and Vietnamese;
  \item a question-template model that supports variables, derived expressions, constraints, and multiple accepted formulas;
  \item persisted question snapshots that separate reusable templates from concrete attempt data;
  \item a progression model combining mastery, XP logs, levels, and achievements;
  \item a dynamic access-control model that separates actions, resources, and subject restrictions.
\end{itemize}

\section{Thesis Structure}

The remainder of this thesis is organized as follows. Chapter 2 presents the requirements and analysis of the project domain. Chapter 3 describes the system design, architecture, security model, and data model. Chapter 4 explains implementation details across the frontend, backend, and database layers. Chapter 5 evaluates the current solution through representative scenarios, strengths, and limitations. Chapter 6 concludes the thesis and outlines future work.
